|

### 2023-01-18 RR_manuscript/supplementary_materials.Rmd
♻️ - render supplementary_materials

```{r}
#| label: sankey-plot
#| fig.cap: "Sankey plot illustrating workflow choices from analyst teams."
#| out.width: "100%"
knitr::include_graphics(path = "./figs/flow_outcome.png")
```

>>>>

```{r}
#| label: sankey-plot
#| fig.cap: "Sankey plot illustrating workflow choices from analyst teams."
#| out.width: "100%"
knitr::include_graphics("../figs/flow_outcome.png", error = FALSE)
```
